
\section{SCENARIO IDENTIFYING}

In this section we will provide the description of some scenarios that may occur using my taxi service:
\begin{enumerate}
	\item Pippo has just arrived to Naples as a tourist, he decides that he wants to go to the cinema, but the cinema is in a place not reachable using public transports, and the movie starts in ten minutes so he can't just walk there. Pippo has heard some rumors of a revolutionary application for managing taxi rides called my taxi service, he googles it, download the application on his phone, register to the system and then log in, then he requests a taxi inserting the address of his current location. The system forwards it to the first taxi available, the driver accept the call and arrives in less than two minutes to pick up Pippo and bring him to the cinema.
	\item Nicholas is coming home to Milan tomorrow, he will arrive at Linate airport and there's no one to pick him up. So he log in to my taxi service and makes a reservation for a taxi inserting Linate as starting position, his home's address as destination and the time he wants to take the ride, let's say two o'clock pm, he then decides to make another reservation from his home to his office, inserting as time twenty minutes past two pm, the system denies the second reservation because he already have a ride occurring less than 30 minutes before. When Nicholas arrives at the airport the taxi is there to pick him up and brings Nicholas home.
	\item Mario wants to take a taxi to go from his home to the theatre, but he doesn't have enough money for a ride, so when making a reservation he enables the taxi sharing option, hoping someone is going in the same direction so they can split the ride's cost. Luigi is willing to go to the same theatre, and he lives not far from Mario, he sees the shared ride created by Mario and joins it, a notification is sent to Mario informing that Luigi joined the ride. Matthew needs to go to his office placed one kilometer north of the theatre, and he joins the ride too. Micheal and Thea need to go in the same direction and they try to join the ride too, but the taxi is already full so the system denies the join request. Mario tries to cancel the shared ride but he can't cause other people has already joined it. Luigi decides he doesn't want to go to the theatre and leave the shared ride, Matthew tries to leave the shared ride too but it's too late so he have to join it. The system now computes a route for the taxi based on all the location provided by the users and send it to the driver, also send to both driver and passenger the cost of the ride.
	\item Oliver has an appointment in 30 minutes, so he decides to make a reservation for a taxi. After completing the form the system denies the reservation because the requested time is not at least two hours later the time Oliver completed the registration form.
	\item Pippo requests a taxi inserting as starting location "Wallaby Way 42 - Sidney", the system does not find this location anywhere on the map and denies the request, asking Pippo a valid location.
	\item Barry requests a taxi inserting his home's address, the system denies it because Barry has a reserved ride occurring in fifteen minutes.
	\item Hooch is a taxi driver, he's waiting in his taxi at a station, he set his availability on and he didn't accept a call or something, suddenly a passenger shows up, Hooch is free so he picks him up, log in the application and set his availability off because he already has a passenger to take care of.
\end{enumerate}